---
title: "Lab 12"
author: "Shawn Santo"
date: "11/25/19"
output: 
  html_document:
    css: lab12.css
    toc: true
    number_sections: false
    toc_float: true
    df_print: paged
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      message = FALSE, 
                      warning = FALSE,
                      comment = NA,
                      fig.width=8, 
                      fig.height=6)
```

## Packages

```{r}
library(sparklyr)
library(tidyverse)
library(wordcloud)
```

## Introduction

As we have seen, `sparklyr` provides an interface for Spark and gives us
the ability to perform data manipulation, Spark SQL queries, and access Spark's
machine learning library. Package `sparklyr` can also facilitate text mining
through Spark. See https://spark.rstudio.com/guides/textmining/ as a reference
for this lab.

Package `sparklyr` allows you to read in text data and perform a number of
feature transformations on said data.

To get started, create a spark connection with 2 cores. Depending on where you
are working you may need to set the argument `spark_home`. Saxon has an
instance of Spark installed under `/data`. Spark is not installed on Trig2.

```{r eval=FALSE}
sc <- spark_connect(master = "local[2]")
```

## Document processing

Select one of the documents below for this lab. You will need to 
download it (`download.file()`),
extract the text (if it is an html or htm document, maybe use `rvest`), 
and save it in your working directory as a `.txt` file.

<b>
Abraham Lincoln <br/>
Gettysburg Address <br/>
November 19, 1863, Address Delivered at the Dedication of the Cemetery at Gettysburg<br/>
</b>
https://www.d.umn.edu/~rmaclin/gettysburg-address.html

<b>
Dr. Martin Luther King Jr.<br/>
I have a dream speech<br/>
August 28, 1963, Lincoln Memorial in Washington D.C.<br/>
</b>
http://www.analytictech.com/mb021/mlk.htm

<b>
Theodore J. Kaczynski aka Unabomber<br/>
Manifesto<br/>
September 19, 1995, The Washington Post<br/>
</b>
https://www.josharcher.uk/static/files/2018/01/Industrial_Society_and_Its_Future-Ted_Kaczynski.txt

## Word cloud

Create a tidy text data frame based on your selected document. The data
frame should have the document's words and their counts. 
This can then be used to create a word cloud with package `wordcloud`. 
Work with `sparklyr`'s functions (`spark_read_text()`, `ft_*()`, etc)
to perform this text mining and cleaning. 
See https://spark.rstudio.com/guides/textmining/ for
reference as to what is available and how to handle regular expressions.
Remember to remove punctuation, numbers, and stop words.

